---
title: "text_book_ch2"
author: "Michael Robinson"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction:

In this lab I will use the code from the reading, to examine Text mining, using three lexicons (bing, nrc, and afinn), I will then use an additional lexicon (loughran) to perform further analysis. I will then create a second R chunk using a different corpus and all four lexicons.

# References

R for Data Science by Hadley Wickham & Garrett Grolemund (2017). Package `tidytext`. Retrieved from <https://www.tidytextmining.com/>

Silge, Julia, PhD. & Robinson, David, PhD. (2017). Text Mining with R: A Tidy Approach. O'Reilly Media, Inc.

```{r Jane Austen}
library(tidytext)
library(janeaustenr)
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(wordcloud)
library(lexicon)
library(textdata)



text_df <- read.csv("/Users/michaelrobinson/Data_607/tweets_data.csv", stringsAsFactors = FALSE, header = TRUE)

get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")
get_sentiments("loughran")

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)

nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)

jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")

pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")

afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  pride_prejudice %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  pride_prejudice %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")

bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)

custom_stop_words <- bind_rows(tibble(word = c("miss"),  
                                      lexicon = c("custom")), 
                               stop_words)

tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))

library(reshape2)

tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)

p_and_p_sentences <- tibble(text = prideprejudice) %>% 
  unnest_tokens(sentence, text, token = "sentences")
p_and_p_sentences$sentence[2]

austen_chapters <- austen_books() %>%
  group_by(book) %>%
  unnest_tokens(chapter, text, token = "regex", 
                pattern = "Chapter|CHAPTER [\\dIVXLC]") %>%
  ungroup()

austen_chapters %>% 
  group_by(book) %>% 
  summarise(chapters = n())

bingnegative <- get_sentiments("bing") %>% 
  filter(sentiment == "negative")

wordcounts <- tidy_books %>%
  group_by(book, chapter) %>%
  summarize(words = n())

tidy_books %>%
  semi_join(bingnegative) %>%
  group_by(book, chapter) %>%
  summarize(negativewords = n()) %>%
  left_join(wordcounts, by = c("book", "chapter")) %>%
  mutate(ratio = negativewords/words) %>%
  filter(chapter != 0) %>%
  slice_max(ratio, n = 1) %>% 
  ungroup()

loughran_lexicon <- get_sentiments("loughran")

loughran_sentiment <- tidy_books %>%
  filter(book == "Sense & Sensibility") %>%  
  inner_join(loughran_lexicon, by = c(word = "word")) %>% 
  count(word, sentiment, sort = TRUE)

loughran_summary <- loughran_sentiment %>%
  group_by(sentiment) %>%
  summarise(total_count = sum(n)) %>%
  ungroup()

#create a bar plot 
ggplot(loughran_summary, aes(x = sentiment, y = total_count, fill = sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Word Counts by Sentiment in 'Sense & Sensibility'",
       x = "Sentiment",
       y = "Total Word Count") +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "none") + coord_flip()
```

## Introduction

In this chunk of the assignment I will use a pdf version on the book A Journey to the center of the earth. I will load the pdf file, then create a corpus and do some text processing. I will then use the lexicons (AFINN,Bing,nrc and loughran) to do analysis on the book and create some visualization.

```{r assignment 10}

library(pdftools)
library(tm)
library(tidytext)
library(dplyr)
library(ggplot2)
library(textdata)
library(RefManageR)

# Reference: 

bib <- BibEntry(
  bibtype = "Book",
  title = "A Journey to the center of the Earth",
  author = "Jules Verne",
  translator = "Fredrick Amadeus Malleson",
  year = "1871", 
  publisher = "Griffith and Farran",
  address = "England"
)

#print(bib)

Book <- "A-Journey-to-the-Centre-of-the-Earth.pdf"

# Read the text from the PDF
journey_cent <- pdf_text(Book)

# Create corpus
document <- Corpus(VectorSource(journey_cent))

# Text preprocessing
document <- tm_map(document, content_transformer(tolower))
document <- tm_map(document, removeNumbers)
document <- tm_map(document, removeWords, stopwords("english"))
document <- tm_map(document, removePunctuation, preserve_intra_word_dashes = TRUE)
document <- tm_map(document, stripWhitespace)

# Create a Document-Term Matrix
Book_Jorney <- DocumentTermMatrix(document)

# Convert the Document-Term Matrix into a tidy format
Book_Jorney_tidy <- tidy(Book_Jorney)
names(Book_Jorney_tidy)[2] <- 'word'       

# Access the lexicons
get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")

# using the Bing lexicon
Book_Jorney_bing <- Book_Jorney_tidy %>%
  inner_join(get_sentiments("bing"), by = c(word = "word"))

# Using the AFINN lexicon
Book_Jorney_afinn <- Book_Jorney_tidy %>%
  inner_join(get_sentiments("afinn"), by = c(word = "word"))

# Filtering the joy words from the NRC lexicon
nrcjoy <- get_sentiments("nrc") %>%
  filter(sentiment == "joy")
Book_Jorney_nrcjoy <- Book_Jorney_tidy %>%
  inner_join(nrcjoy) %>%
  count(word, sort = TRUE)

# Filtering the fear words from the NRC lexicon 
nrcfear <- get_sentiments("nrc") %>%
  filter(sentiment == "fear")
Book_Jorney_nrcfear <- Book_Jorney_tidy %>%
  inner_join(nrcfear) %>%
  count(word, sort = TRUE)

# create a frequency count for the Bing lexicon
Book_Jorney_bing_count <- Book_Jorney_bing %>%
  count(word, sentiment, sort = TRUE)

# AFINN lexicon, sum the scores for each word
Book_Jorney_afinn_sum <- Book_Jorney_afinn %>%
  group_by(word) %>%
  summarize(score_sum = sum(value, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(score_sum))

# Calculate the count of each sentiment score
Book_Jorney_afinn_count <- Book_Jorney_afinn %>%
  group_by(value) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  arrange(desc(count))

# Calculate the frequency of words that have an AFINN score
Book_Jorney_afinn_frequency <- Book_Jorney_afinn %>%
  count(word, sort = TRUE)

# Bar plot for Bing lexicon
Book_Jorney_bing_count %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)

# Bar plot for AFINN lexicon
ggplot(Book_Jorney_afinn_count, aes(x = value, y = count)) +
  geom_bar(stat = "identity", aes(fill = value > 0)) +  # Color bars by positive or negative sentiment
  scale_fill_manual(values = c("red", "green"), name = "Sentiment", 
                    labels = c("Negative", "Positive")) +
  labs(x = "AFINN Sentiment Score", y = "Count", title = "Counts of AFINN Sentiment Scores") +
  theme_minimal() +
  theme(legend.position = "bottom")

Book_Jorney_nrcjoy <- Book_Jorney_nrcjoy %>% 
  arrange(desc(n))

# Create a wordcloud of nrc joy words

wordcloud(words = Book_Jorney_nrcjoy$word,
          freq = Book_Jorney_nrcjoy$n,
          min.freq = 1,
          max.words = 145,
          random.order = FALSE,
          rot.per = 0.35,
          scale = c(4, 0.5),
          colors = brewer.pal(8, "Dark2"))

# Create a wordcloud of nrc fear words

Book_Jorney_nrcfear <- Book_Jorney_nrcfear %>% 
  arrange(desc(n))

wordcloud(words = Book_Jorney_nrcfear$word,
          freq = Book_Jorney_nrcfear$n,
          min.freq = 1,
          max.words = 110,
          random.order = FALSE,
          rot.per = 0.35,
          scale = c(4, 0.5),
          colors = brewer.pal(8, "Dark2"))


loughran_lexicon <- get_sentiments("loughran")


Book_Journey_loughran <- Book_Jorney_tidy %>%
  inner_join(loughran_lexicon, by = c(word = "word"))

# Count the frequency of each sentiment
Book_Journey_loughran_count <- Book_Journey_loughran %>%
  count(sentiment, sort = TRUE) %>%
  mutate(lexicon = "Loughran-McDonald") # Add a column for the lexicon name


ggplot(Book_Journey_loughran_count, aes(x = sentiment, y = n, fill = sentiment)) + 
  geom_bar(stat = "identity") + 
  labs(x = "Sentiment", y = "count", title = " Counts of Sentiments (Loughran-McDonald Lexicon)") + theme_minimal() + coord_flip()

```
